Robust Bayesian Analysis of Causal Inference Problems

### 2022-10-31 JASA-template.tex
some corrections

We fix sufficiently small $\tau^2_0$
$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
To construct the slab component, we consider $\tau_1^2$ to be large so that 
$\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat.

As mentioned earlier, $\pi_j$ is used as the rejection probability
of the $j$-th predictor and we use a set beta priors to specify 
these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
a concentration parameter.
For the intercept terms of the outcome model and the causal effect, 
we consider a sufficiently flat prior so that 
$\beta_0. \beta_T\sim \normal(0,\sigma^2)$. Similarly, for the
intercept term in the treatment model, we consider 
$\gamma_0\sim \normal(0,1)$.

>>>>

We fix sufficiently small $\tau^2_0$
$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
To construct the slab component, we consider $\tau_1^2$ to be large so that $\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat. Inverse-Gamma is a natural choice
for the variance of the Gaussian noise because of conjugacy. To
make the prior flat, we consider $1\gg a, b >0$.

As indicated earlier, $\pi_j$ is used as the rejection probability
of the $j$-th predictor and we use a beta prior to specify 
these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
a concentration parameter.
For the intercept terms of the outcome model and the causal effect, 
we consider a sufficiently flat prior so that 
$\beta_0. \beta_T\sim \normal(0,\sigma^2)$. Similarly, for the
intercept term in the treatment model, we consider 
$\gamma_0\sim \normal(0,1)$.

In \cref{fig:regress}, we show a probabilistic graphical representation
of our hierarchical model. In the figure, grey circular nodes represent the
prior hyper-parameters which will be used for sensitivity analysis
of the model. The transparent circular nodes are used to denote
the modelling parameters which are our quantities of interest. 
The observed quantities are denoted with transparent rectangular
nodes. We also use a grey rectangular node to denote the intermediate
latent variable $T^*$. We use directed edges to denote the
relationship between different nodes. However, we use a dashed
edge between $X$ and $T$ as we they are related through the latent
variable $T^*$. This dashed edge also establish the notion of
confounding as shown in \cref{fig:confounding}.
